---
output: rmarkdown::github_document
---

# roto.s3

Access and Orchestrate Amazon Simple Storage Service

## Description

This is a 'reticulated' wrapper for the 'Python' 'boto3' 'AWS' 'S3' client library <https://boto3.readthedocs.io/en/latest/reference/services/s3.html>. It requires 'Python' version 3.5+ and an 'AWS' account.

## What's Inside The Tin

The following functions are implemented: _(more to come)_

- `download_file`:	Download an S3 object to a file.
- `upload_file`:	Upload a file to an S3 object.

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/roto.s3")
# OR
devtools::install_git("git://gitlab.com/hrbrmstr/roto.s3")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(roto.s3)
library(tidyverse)

# current verison
packageVersion("roto.s3")

```

```{r echo=FALSE}
suppressMessages(suppressWarnings(unlink("/tmp/mtcars.csv", force=TRUE)))
suppressMessages(suppressWarnings(unlink("/tmp/mtcars-01.csv", force=TRUE)))
```

### Upload

```{r}
write_csv(mtcars, "/tmp/mtcars.csv")

upload_file(
  filename = "/tmp/mtcars.csv", 
  bucket = "is.rud.test", 
  key = "mtcars.csv",
  profile_name = "personal"
)
```

### Download

```{r}
download_file(
  bucket = "is.rud.test", 
  key = "mtcars.csv", 
  filename = "/tmp/mtcars-again.csv", 
  profile_name = "personal"
)

read_csv("/tmp/mtcars-again.csv")
```




